% Updated 2019-11-26
\documentclass[letterpaper,11pt]{cv_format}
\usepackage{hyperref}
\usepackage{array}
\usepackage{longtable,tabularx}
\usepackage{graphicx}
\usepackage{changepage}
\begin{document}
\name{Adrian Danao-Schroeder}
\textbf{\centering B.S. Aerospace Engineering \hspace{1cm}\textperiodcentered\hspace{1cm}  B.A. Chinese\\}

\contact{Silver Spring, MD, 20910}{adriandanao@gmail.com}{\href{https://adriandanao.com/}{adriandanao.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\datedsubsection{University of Maryland College Park}{GPA. 3.24}
\vspace{-2em}
\begin{adjustwidth}{10em}{0em}
\begin{longtable}{p{.2\linewidth} p{.838\linewidth} rp{.05\linewidth} rp{.15\linewidth}}
Bachelor of Science & Aerospace Engineering & May & 2019 \\
Bachelor of Arts  & Chinese & Aug. & 2019
\end{longtable}
\end{adjustwidth}
\vspace{-2em}
\textbf{\emph{Relevant Courses:}} Space Propulsion, Space System Design, Mechanics of Composites, Linear Controls, Vibrations and Aeroelasticity, Dynamics of Aerospace Systems, Space Flight Dynamics, Aerodynamics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\datedsubsection{Link Coder, \small{American Immigration Lawyers Association}}{Aug. -- Oct. 2019}
\begin{c_itemize}
    \item Worked on document conversion code to convert completed legal documents to HTML for online publication
    \item Wrote documentation and maintenance manuals for existing document conversion and database management
    \item Created an automated and manual lookup tool to link document references to an online document database 
    \item Reduced time to review converted HTML documents from 2 business days to 2 hours
\end{c_itemize}

\datedsubsection{Software Licensing Associate, \small{Univertsity of Maryland Division of IT}}{Feb. 2016 -- Sep.2018}
\begin{c_itemize}
    \item Licensed and managed software contracts, distribution and maintenance for the University of Maryland
    \item Administered the University of Marylands software distribution service
    \item Provided technical support and troubleshooting for problems related to software installation and licensing 
    \item Hired and trained new staff members to manage distribution and provide technical support to faculty and staff

\end{c_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\datedsubsection{Deployable Heat Shield, {\small Space Systems Laboratory}}{Jul. 2018 -- Jul. 2019 }
\begin{c_itemize}
    \item Designed a deployable heat shield to recover a 3U CubeSat from low earth orbit
    \item Simulated reentry conditions and flow over heat shield at hypersonic reentry velocities
    \item Used methods of characteristics and ANSYS Fluent CFD, to determine ballistic coefficients, flight trajectory and passive stability in hypersonic, supersonic and subsonic flight
\end{c_itemize}

\datedsubsection{Terrapin Rockets Development Team, \small{\emph{Propulsion Team}}}{Oct. 2017 -- May 2019 }
\begin{c_itemize}
    \item Developed a paraffin and liquid N$_2$O hybrid rocket motor and test stand capable of producing 200 lb. of thrust
    \item Utilized ANSYS Fluent and CHEMKIN to simulate combustion chamber dynamics to determine regression rates, predicted chamber pressure and temperature for the small scale test stand
    \item Designed hybrid rocket motor rocket to push a 8.5kg to 30,000 ft. for the Spaceport America Cup
\end{c_itemize}

\datedsubsection{CanSat Competition 2018 Deployable Heat Shield}{Oct. 2017 -- Jun. 2018}
\begin{c_itemize}
    \item Designed and built a rocket launched probe to test and simulate a deployable heat shield to slow probes descent 
    \item Used ANSYS Fluent CFD simulations of descent rate and stability of probe and heat shield during flight to modify the design accurately determine the flight characteristics
    \item Placed 4$^{th}$ among 104 international teams competing in competition
\end{c_itemize}

\datedsubsection{Flight Controller for Propulsive Landing, Control of Aerospace Systems}{May 2018}
\begin{c_itemize}
    \item Developed a flight control algorithm to land a simulated rocket on a moving barge
    \item Flight controller implemented noise pre-filtering, external disturbance rejection and second order target tracking
\end{c_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbf{Programs:}ANSYS (Fluent, FEA, CHEMKIN), Siemens NX, NASTRAN, STK, SolidWorks, AutoCAD, MATLAB \\
\textbf{Fabrication Skills:}Welding (TIG and Stick), Lathe, Milling, General Shop Machines\\
\textbf{Programming Languages:} Python, C++, Java, HTML, CSS,  JavaScript, Ruby, \LaTeX\\
\textbf{Foreign Languages:}Spanish (Native Fluency), Chinese (6 years of study)

 
\end{document}